Implementation and assessment of tools for integrating forest roads into projections of the cumulative effects of disturbance on wildlife

### 2024-04-02 analysis/paper/paper.Rmd
working on paper fig 2, syncing first

# read in example area data
exRoads <- read_sf(here(data_path_drvd, "..", "testing_ex_roads.gpkg"))
tsb <- read_sf(here(data_path_drvd, "..", "testing_tsb.gpkg"))
cutblocks <- read_sf(here(data_path_drvd, "..", "testing_cutblocks.gpkg"))
tsaCost <- raster::raster(here(data_path_drvd, "..", "testing_cost.tif"))
roads <- read_sf(here(data_path_drvd, "..", "testing_obs_roads.gpkg"))

@@

@@

allProj <- bind_rows(mstProj, ilcpProj, .id = "method") %>%
  arrange(desc(sampleType), sampleDens)

@@

allProj <- bind_rows(
  allProj,
  tibble(sampleType = "", sampleDens = 0, method = "Hardy QGIS",
             output = list(here(data_path_drvd, "..", "for_fig", 
                                "HardyQGISTest.gpkg")))) %>% 
  mutate(mapTitle =  paste(ifelse(method == 1, "MST",
                                  ifelse(method == 2, "ILCP", method)),
                           sampleType,
                           ifelse(sampleDens == 1e-06 & 
                                    sampleType != "centroid", "low density", 
                                  ifelse(sampleDens == 1e-05, 
                                         "high density", ""))))

>>>>

# read in example area data
exRoads <- read_sf(here(data_path_drvd, "..", "testing_ex_roads.gpkg"))
tsb <- read_sf(here(data_path_drvd, "..", "testing_tsb.gpkg"))
cutblocks <- read_sf(here(data_path_drvd, "..", "testing_cutblocks.gpkg"))
tsaCost <- raster::raster(here(data_path_drvd, "..", "testing_cost.tif"))
dem <- raster::raster(here(data_path_drvd, "..", "testing_dem.tif"))
roads <- read_sf(here(data_path_drvd, "..", "testing_obs_roads.gpkg"))

@@

simpleCostFn = function(x1,x2,...) (x1+x2)/2
paramTable$weightFunction = deparse1(simpleCostFn,collapse="\n")
paramTable$weightMethod = "simple cost"

paramTableDem = paramTable
paramTableDem$weightFunction = deparse1(slopePenaltyFn,collapse="\n")
paramTableDem$weightFunction = gsub("limitWeight = NA","limitWeight = 65000",paramTableDem$weightFunction,fixed=T)

@@

# re-run projections for just the small area with different parameters
mstProjDem <- projectAll(tsbs = tsb, paramTable = paramTableDem,
                      weightRaster = dem,
                      cutblocks = cutblocks,
                      existingRoads = exRoads,
                      fileLocation = here(data_path_drvd, "..", "for_fig"),
                      roadsInWeight = F)

ilcpProjDem <- projectAll(tsbs = tsb,
                      paramTable = paramTableDem %>% 
                        filter(sampleType == "regular") %>% 
                        mutate(method = "ilcp"),
                      weightRaster = dem,
                      cutblocks = cutblocks,
                      existingRoads = exRoads,
                      fileLocation = here(data_path_drvd, "..", "for_fig"),
                      roadsInWeight = F)

allProj <- bind_rows(mstProj, ilcpProj, mstProjDem, ilcpDem, .id = "method") %>%
  arrange(desc(sampleType), sampleDens)

@@

allProj <- bind_rows(
  allProj,
  tibble(sampleType = "", sampleDens = 0, method = "Hardy QGIS",
             output = list(here(data_path_drvd, "..", "for_fig", 
                                "HardyQGISTest.gpkg")))) %>% 
  mutate(mapTitle =  paste(ifelse(method == 1, "MST",
                                  ifelse(method == 2, "ILCP", method)),
                           weightMethod,
                           sampleType,
                           ifelse(sampleDens == 1e-06 & 
                                    sampleType != "centroid", "low density", 
                                  ifelse(sampleDens == 1e-05, 
                                         "high density", ""))))
